Meta-analysis of the Interoceptive Accuracy Scale (IAS)

### 2025-01-03 analysis/Stud1_a.qmd
added Giulias data
rendered html with added data

- Arslanova (2022)
  - https://osf.io/mp3cy/

```{r}
df5 <- readxl::read_excel("../data/Arslanova2022/Murphy_Iacc_scale.xlsx")  |> 
  filter(str_detect(Question.Key, "IAC_")) |> 
  filter(str_detect(Question.Key, "-quantised")) |> 
  pivot_wider(names_from = Question.Key, values_from = Response) |>
  rename_with(\(x) str_remove(x, "IAC_"), .cols = starts_with("IAC_")) |> 
  rename_with(\(x) str_remove(x, "-quantised"), .cols = everything()) |> 
  rename(Sex_arousal = SexuallyAroused, Itch = Itchy, Sex_arousal = SexuallyAroused,
         Temp = HotCold, Tickle = Ticklish, Breathing= BreatheFast, 
         Affective_touch= PleasantAffectionate, Blood_Sugar= BloodSugar, 
         Muscles=TiredMuscles, Heart= FastHeart, Taste=Tastes) |> 
  select(-starts_with("Participant")) |> 
  mutate_all(as.numeric)
```

@@

- Makowski
  - Note: First sample has some missing items
  - Note: Analog scales

@@

# Save all
data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10a=df10a, df10b=df10b)
save(data, file = "../data/data.RData")
```

@@

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10a**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10b**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10b, age = "Age", sex = NA, gender = "Gender")`.

Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10a) + nrow(df10b)`.

@@

desc_df1a <- desc(df1a)
desc_df1b <- desc(df1b)
desc_df2 <- desc(df2)
desc_df3 <- desc(df3)
#desc_df4 <- desc(df4)
#desc_df5 <- desc(df5)
desc_df6 <- desc(df6)
desc_df7a <- desc(df7a)
desc_df7b <- desc(df7b)
desc_df7c <- desc(df7c)
desc_df8a <- desc(df8a)
desc_df8b <- desc(df8b)
desc_df9 <- desc(df9)
desc_df10a <- desc(df10a)
desc_df10b <- desc(df10b)

desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10a, desc_df10b)

@@

# Create the dataframe
table <- data.frame(
  Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Total'),
  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', ''),
  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), 96, nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), 31317),
  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "TODO*", "TODO*", make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), 49.5),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76', '17 - 93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', NA, '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '71.5%'),
  Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', '')
)

table_apa <- table |> 
  gt() |>
  cols_align(align = c("right"), columns = "Age") |> 
  cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
  tab_footnote("* Information copied from the sample description rather than recomputed.") |> 
  gt_apastyle()

@@

dens1a <- estimate_density(select(df1a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1a")
dens1b <- estimate_density(select(df1b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1b")
dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 2")
dens3 <- estimate_density(select(df3, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 3")
dens4 <- estimate_density(select(df4, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 4")
dens5 <- estimate_density(select(df5, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 5")
dens6 <- estimate_density(select(df6, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 6")
dens7a <- estimate_density(select(df7a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7a")
dens7b <- estimate_density(select(df7b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7b")
dens7c <- estimate_density(select(df7c, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7c")
dens8a <- estimate_density(select(df8a, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 8a")
dens8b <- estimate_density(select(df8b, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 8b")
dens9 <- estimate_density(select(df9, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 9")
dens10a <- estimate_density(select(df10a, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
  mutate(Sample = "Sample 10a",
         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
dens10b <- estimate_density(select(df10b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 10b",
         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))

p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b) |>
  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b")) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  scale_color_material_d() +
  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold")) +
  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free_y", nrow = 5)

@@

```{r}
data1a <- normalize(select(df1a, all_of(dens1a$Parameter)), range = c(1, 5))
data1b <- normalize(select(df1b, all_of(dens1b$Parameter)), range = c(1, 5))
data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
data4 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
data6 <- normalize(select(df6, all_of(dens6$Parameter)), range = c(1, 5))
data7a <- normalize(select(df7a, all_of(dens7a$Parameter)), range = c(1, 5))
data7b <- normalize(select(df7b, all_of(dens7b$Parameter)), range = c(1, 5))
data7c <- normalize(select(df7c, all_of(dens7c$Parameter)), range = c(1, 5))
data8a <- normalize(select(df8a, all_of(dens8a$Parameter)), range = c(1, 5))
data8b <- normalize(select(df8b, all_of(dens8b$Parameter)), range = c(1, 5))
data9 <- normalize(select(df9, all_of(dens9$Parameter)), range = c(1, 5))
data10a <- select(df10a, all_of(dens10a$Parameter))
data10b <- select(df10b, all_of(dens10b$Parameter))

data_all <- rbind(
  data1a, data1b, data2, data3, data4, data5, data6, data7a, data7b, data7c,
  mutate(data8a, Tickle = NA), mutate(data8b, Tickle = NA), data9,
  mutate(data10a, Taste = NA, Cough = NA, Blood_Sugar = NA), data10b
) 
```

@@

@@

@@

@@

@@

>>>>

- Arslanova (2022)
  - https://osf.io/mp3cy/
  - note: Final.xlsx includes information about which participants passed the attention checks

df5_attention <- readxl::read_excel("C:/Users/asf25/Documents/studies/InteroceptionIAS/data/Arslanova2022/Participants2.xlsx", 
    sheet = "FINAL") |>
  filter(ActorHR == 1) |>
  select(Subj.ID, Gender, Age) |>
  mutate(Gender = as.numeric(Gender), Age = as.numeric(Age)) |>
  filter(!is.na(Age)) |> #error on the documentation of this participant - attention check failed but not noted
  mutate(Gender = case_when(
    Gender== 0 ~ "Male",
    Gender== 1 ~ "Female" # based on paper reporting 65 women
  ))

df5 <- readxl::read_excel("../data/Arslanova2022/Murphy_Iacc_scale.xlsx")  |>
  filter(str_detect(Question.Key, "IAC_")) |> 
  filter(str_detect(Question.Key, "-quantised")) |> 
  pivot_wider(names_from = Question.Key, values_from = Response) |>
  rename_with(\(x) str_remove(x, "IAC_"), .cols = starts_with("IAC_")) |> 
  rename_with(\(x) str_remove(x, "-quantised"), .cols = everything()) |> 
  rename(Sex_arousal = SexuallyAroused, Itch = Itchy, Sex_arousal = SexuallyAroused,
         Temp = HotCold, Tickle = Ticklish, Breathing= BreatheFast, 
         Affective_touch= PleasantAffectionate, Blood_Sugar= BloodSugar, 
         Muscles=TiredMuscles, Heart= FastHeart, Taste=Tastes) |> 
  rename(Subj.ID = "Participant.Public.ID") |>
  select(-starts_with("Participant"))

df5 <- df5 |>
  filter(Subj.ID %in% df5_attention$Subj.ID) |>
  select(-Subj.ID) |>
  mutate(across(everything(), as.numeric))

@@

- Makowski
  - Note: First sample has some missing items
  - Note: Analog scales
  - note df10c = primals data

@@

df10c <- read.csv("https://raw.githubusercontent.com/RealityBending/InteroceptionPrimals/refs/heads/main/data/data_participants.csv") |>
  select("Participant" = "participant_id", "Gender", "Age", "Ethnicity", starts_with("IAS")) |>
   rename(
    Heart = IAS_1, Hungry = IAS_2, Breathing = IAS_3, Thirsty = IAS_4,
    Urinate = IAS_5, Defecate = IAS_6, Taste = IAS_7, Vomit = IAS_8, Sneeze = IAS_9,
    Cough = IAS_10, Temp = IAS_11, Sex_arousal = IAS_12, Wind = IAS_13, Burp = IAS_14,
    Muscles = IAS_15, Bruise = IAS_16, Pain = IAS_17, Blood_Sugar = IAS_18,
    Affective_touch = IAS_19, Tickle = IAS_20, Itch = IAS_21
  ) |>
  filter(!is.na(Heart)) # participant is outlier and had total IAS scores below 0.4

### Sample 11

- Giulia

df11a <- df11a <- haven::read_sav("../data/Giulia/Interoceptive Attention ESM.sav") |> 
  select(AGE, GENDER, contains("IAS_ACC"), -IAS_ACC_20) |>
  mutate_all(as.numeric) |>
  rename(
    Age = AGE, Gender = GENDER,
    Heart = IAS_ACC_1, Hungry = IAS_ACC_2, Breathing = IAS_ACC_3, Thirsty = IAS_ACC_4,
    Urinate = IAS_ACC_5, Defecate = IAS_ACC_6, Taste = IAS_ACC_7, Vomit = IAS_ACC_8, Sneeze = IAS_ACC_9,
    Cough = IAS_ACC_10, Temp = IAS_ACC_11, Sex_arousal = IAS_ACC_12, Wind = IAS_ACC_13, Burp = IAS_ACC_14,
    Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18,
    Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_21, Itch = IAS_ACC_22
  ) |>
   mutate(Gender = case_when(
    Gender == 1 ~ "Male",
    Gender == 2 ~ "Female",
    Gender %in% c(3, 5) ~ "Other",
    Gender == 4 ~ "NA"
  ))

df11b <- haven::read_sav("../data/Giulia/Sleep and Exteroceptive Interoceptive Sensitivity.sav") |> # 165 participants
  filter(Total_Attention_Fail == 0) |> # 32 participants removed based on failing one or more checks
  select(AGE, GENDER, contains("IAS_ACC")) |> 
  mutate_all(as.numeric) |> 
  rename( Age = AGE, Gender = GENDER, 
          Heart = IAS_ACC_1, Hungry = IAS_ACC_2, Breathing = IAS_ACC_3, Thirsty = IAS_ACC_4, Urinate = IAS_ACC_5, Defecate = IAS_ACC_6, Taste = IAS_ACC_7,
          Vomit = IAS_ACC_8, Sneeze = IAS_ACC_9, Cough = IAS_ACC_10, Temp = IAS_ACC_11, Sex_arousal = IAS_ACC_12, Wind = IAS_ACC_13, Burp = IAS_ACC_14,
          Muscles = IAS_ACC_15, Bruise = IAS_ACC_16, Pain = IAS_ACC_17, Blood_Sugar = IAS_ACC_18, Affective_touch = IAS_ACC_19, Tickle =IAS_ACC_20, 
          Itch = IAS_ACC_21 )  |> 
  mutate(Gender = case_when(
    Gender == 1 ~ "Male", 
    Gender == 2 ~"Female", 
    Gender %in% c(3, 5) ~ "Other", 
    Gender == 4 ~ "NA", ))

# Save all
data <- list(df1a=df1a, df1b=df1b, df2=df2, df3=df3, df4=df4, df5=df5, df6=df6, df7a=df7a, df7b=df7b, df7c=df7c, df8a=df8a, df8b=df8b, df9=df9, df10a=df10a, df10b=df10b, df10c=df10c, df11a=df11a, df11b=df11b)
save(data, file = "../data/data.RData")
```

@@

- **Sample 1a**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 1, downloaded from OSF, included `r report::report_participants(df1a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 1b**: Data from [Murphy's (2020)](https://osf.io/3m5nh/?view_only=a68051df4abe4ecb992f22dc8c17f769) study 6, downloaded from OSF, included `r report::report_participants(df1b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 2**: Data from [Gaggero's(2020)](https://osf.io/5x9sg/) study, downloaded from OSF, included `r report::report_participants(df2[c("Age", "Gender")], age = "Age", sex = NA, gender = "Gender")`.
- **Sample 3**: Data from [Campos's(2022)](https://osf.io/j6ef3) study, downloaded from OSF, included `r report::report_participants(df3, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 4**: Data from [Todd's(2022)]( https://osf.io/ms354/) study, downloaded from OSF, included `r report::report_participants(df4, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 5**: Data from [Arslanova (2022)](https://osf.io/mp3cy/) study, downloaded from OSF, included `r report::report_participants(df5_attention, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 6**: Data from [Brand's(2022)](https://osf.io/xwz6g/) study, downloaded from OSF, included `r report::report_participants(df6, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7a**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7b**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 7c**: Data from [Brand's(2023)](https://osf.io/3f2h6/) study, downloaded from OSF, included `r report::report_participants(df7c, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8a**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 8b**: Data from [Lin's(2023)](https://osf.io/3eztd) study, downloaded from OSF, included `r report::report_participants(df8b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 9**: Data from [VonMohr's(2023)](https://osf.io/7p9u5/) study 3, downloaded from OSF, included `r report::report_participants(df9, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10a**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10a, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10b**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10b, age = "Age", sex = NA, gender = "Gender")`.
- **Sample 10c**: Data from [Makowski's(2023)] study , downloaded from OSF, included `r report::report_participants(df10c, age = "Age", sex = NA, gender = "Gender")`.
-- **Sample 11a**: Data from [Giulia's (2024)](https://osf.io/49wbv) study , included `r report::report_participants(df11a, age = "Age", sex = NA, gender = "Gender")`
- **Sample 11b**: Data from [Giulia] study , included `r report::report_participants(df11b, age = "Age", sex = NA, gender = "Gender")`

Total N = `r nrow(df1a) + nrow(df1b) + nrow(df2) + nrow(df3) + nrow(df4) + nrow(df5) + nrow(df6) + nrow(df7a) + nrow(df7b) + nrow(df7c) + nrow(df8a) + nrow(df8b) + nrow(df9) + nrow(df10a) + nrow(df10b) + nrow(df10c) +nrow(df11a) + nrow(df11b)`.

@@

desc_df1a <- desc(df1a)
desc_df1b <- desc(df1b)
desc_df2 <- desc(df2)
desc_df3 <- desc(df3)
#desc_df4 <- desc(df4)
desc_df5 <- desc(df5_attention)
desc_df6 <- desc(df6)
desc_df7a <- desc(df7a)
desc_df7b <- desc(df7b)
desc_df7c <- desc(df7c)
desc_df8a <- desc(df8a)
desc_df8b <- desc(df8b)
desc_df9 <- desc(df9)
desc_df10a <- desc(df10a)
desc_df10b <- desc(df10b)
desc_df10c <- desc(df10c)
desc_df11a <- desc(df11a)
desc_df11b <- desc(df11b)

desc_total <- rbind(desc_df1a, desc_df1b, desc_df2, desc_df3, desc_df5, desc_df6, desc_df7a, desc_df7b, desc_df7c, desc_df8a, desc_df8b, desc_df9, desc_df10a, desc_df10b, desc_df10c, desc_df11a, desc_df11b)

@@

# Create the dataframe
table <- data.frame(
   Sample = c('Murphy et al., (2020)', '', '', 'Gaggero et al., (2021)', 'Campos et al., (2022)', 'Todd et al., (2022)', 'Arslanova et al., (2022)', 'Brand et al., (2022)', 'Brand et al., (2023)', '', '', '', 'Lin et al., (2023)', '', '', 'VonMohr et al., (2023)', 'Makowski et al., (2023a)', 'Makowski et al., (2023b)', 'Makowski et al., (2023c)', 'Poreiro et al., (2024)', 'Poreiro et al., unpublished', 'Total'),
  Subsample = c('', 'Sample 1', 'Sample 2', '', '', '', '', '', '', 'Sample 1', 'Sample 2', 'Sample 3', '', 'Sample 1', 'Sample 2', '', '', '', '', '','', ''),   
  Language = c('', 'English', 'English' , 'English and Italian', 'Portuguese', 'English', 'English', 'German', '', 'German', 'German', 'German', '', 'Chinese', 'Chinese', 'English', 'English', 'English', 'English', 'English', 'English',''),
  N = c('', nrow(df1a), nrow(df1b), nrow(df2), nrow(df3), nrow(df4), nrow(df5_attention), nrow(df6),'', nrow(df7a), nrow(df7b), 802,'', nrow(df8a), nrow(df8b), nrow(df9), nrow(df10a), nrow(df10b), nrow(df10c), nrow(df11a), nrow(df11b), 32216),
  Age = c('', make_age(df1a$Age), make_age(df1b$Age), make_age(df2$Age), make_age(df3$Age), "48.6.6 ± 14.1*", make_age(df5_attention$Age), make_age(df6$Age),'', make_age(df7a$Age), make_age(df7b$Age), make_age(df7c$Age),'', make_age(df8a$Age), make_age(df8b$Age), make_age(df9$Age), make_age(df10a$Age), make_age(df10b$Age), make_age(df10c$Age), make_age(df11a$Age), make_age(df11b$Age), '48.6 ± 13.1'),
  Range = c('', '18-69', '18-91', '18-58', '18-72', '18-92*', '18-73', '18-78', '', '18-79', '16-81', '18-72','', '16-60', '20-60', '18-93', '18-73', '17-76','18-50', '18-57', '18-60', '17-93'),
  Female_Percentage = c('', '69.4%', '70.1%', '60.3%', '59.6%', '50%*', '46.8%', '78.7%', '', '79.5%', '77.7%', '68.9%', '', '57.0%', '56.2%', '73.2%', '50.3%', '53.0%', '76%', '74.8%', '75.9%', '71.6'),
  Availability= c('', '', 'https://osf.io/3m5nh', 'https://osf.io/5x9sg', 'https://osf.io/j6ef3', 'https://osf.io/ms354', 'https://osf.io/mp3cy', 'https://osf.io/xwz6g', '', '', 'https://osf.io/3f2h6', '','','', 'https://osf.io/3eztd', 'https://osf.io/7p9u5', 'https://github.com/RealityBending/IllusionGameReliability', 'https://github.com/DominiqueMakowski/PHQ4R', 'https://github.com/RealityBending/InteroceptionPrimals', 'https://osf.io/49wbv', '','')
)

table_apa <- table |> 
  gt() |>
  cols_align(align = c("right"), columns = "Age") |> 
  cols_label(Age = "Age (Mean  ± SD)", Female_Percentage = "Female %") |> 
  tab_footnote("* Information taken from the sample description of relevant paper rather than recomputed.") |> 
  gt_apastyle()

@@

dens1a <- estimate_density(select(df1a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1a")
dens1b <- estimate_density(select(df1b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 1b")
dens2 <- estimate_density(select(df2, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 2")
dens3 <- estimate_density(select(df3, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 3")
dens4 <- estimate_density(select(df4, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 4")
dens5 <- estimate_density(select(df5, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 5")
dens6 <- estimate_density(select(df6, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 6")
dens7a <- estimate_density(select(df7a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7a")
dens7b <- estimate_density(select(df7b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7b")
dens7c <- estimate_density(select(df7c, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 7c")
dens8a <- estimate_density(select(df8a, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 8a")
dens8b <- estimate_density(select(df8b, all_of(setdiff(vars, "Tickle"))), method = "kernSmooth") |>
  mutate(Sample = "Sample 8b")
dens9 <- estimate_density(select(df9, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 9")
dens10a <- estimate_density(select(df10a, all_of(setdiff(vars, c("Taste", "Cough", "Blood_Sugar")))), method = "kernSmooth") |>
  mutate(Sample = "Sample 10a",
         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
dens10b <- estimate_density(select(df10b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 10b",
         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
dens10c <- estimate_density(select(df10c, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 10c",
         x = datawizard::rescale(x, to=c(1, 5), range=c(0, 1)))
dens11a <- estimate_density(select(df11a, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 11a")
dens11b <- estimate_density(select(df11b, all_of(vars)), method = "kernSmooth") |>
  mutate(Sample = "Sample 11b")

p1 <- rbind(dens1a, dens1b, dens2, dens3, dens4, dens5, dens6, dens7a, dens7b, dens7c, dens8a, dens8b, dens9, dens10a, dens10b, dens10c, dens11a, dens11b) |>
  mutate(Sample = fct_relevel(Sample, "Sample 1a", "Sample 1b", "Sample 2", "Sample 3", "Sample 4", "Sample 5", "Sample 6", "Sample 7a", "Sample 7b", "Sample 7c", "Sample 8a", "Sample 8b", "Sample 9", "Sample 10a", "Sample 10b", "Sample 10c", "Sample 11a", "Sample 11b")) |>
  # mutate(Dashed = ifelse(Parameter %in% c("Affective_touch", "Blood_Sugar", "Bruise"), TRUE, FALSE)) |> 
  ggplot(aes(x = x, y = y, color = Parameter)) +
  geom_line() +
  scale_color_material_d() +
  scale_linetype_manual(values = c("solid", "dashed"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        plot.title = element_text(face="bold")) +
  labs(title = "Distribution of responses for all items across various datasets", x = "Response", y = "Density", color = "Item") +
  facet_wrap(~Sample, scales = "free_y", nrow = 5)

@@

```{r}
data1a <- normalize(select(df1a, all_of(dens1a$Parameter)), range = c(1, 5))
data1b <- normalize(select(df1b, all_of(dens1b$Parameter)), range = c(1, 5))
data2 <- normalize(select(df2, all_of(dens2$Parameter)), range = c(1, 5))
data3 <- normalize(select(df3, all_of(dens3$Parameter)), range = c(1, 5))
data4 <- normalize(select(df4, all_of(dens4$Parameter)), range = c(1, 5))
data5 <- normalize(select(df5, all_of(dens5$Parameter)), range = c(1, 5))
data6 <- normalize(select(df6, all_of(dens6$Parameter)), range = c(1, 5))
data7a <- normalize(select(df7a, all_of(dens7a$Parameter)), range = c(1, 5))
data7b <- normalize(select(df7b, all_of(dens7b$Parameter)), range = c(1, 5))
data7c <- normalize(select(df7c, all_of(dens7c$Parameter)), range = c(1, 5))
data8a <- normalize(select(df8a, all_of(dens8a$Parameter)), range = c(1, 5))
data8b <- normalize(select(df8b, all_of(dens8b$Parameter)), range = c(1, 5))
data9 <- normalize(select(df9, all_of(dens9$Parameter)), range = c(1, 5))
data10a <- select(df10a, all_of(dens10a$Parameter))
data10b <- select(df10b, all_of(dens10b$Parameter))
data10c <- select(df10c, all_of(dens10c$Parameter))
data11a <- normalize(select(df11a, all_of(dens11a$Parameter)), range = c(1, 5))
data11b <- na.omit(normalize(select(df11b, all_of(dens11b$Parameter)), range = c(1, 5)))
row.names(data11b) <- NULL

data_all <- rbind(
  data1a, data1b, data2, data3, data4, data5, data6, data7a, data7b, data7c,
  mutate(data8a, Tickle = NA), mutate(data8b, Tickle = NA), data9,
  mutate(data10a, Taste = NA, Cough = NA, Blood_Sugar = NA),  data10b,  data10c, data11a, data11b
) 
```

@@

#### Sample 10c

```{r}
make_correlation(data10c)
```

#### Sample 11a

```{r}
make_correlation(data11a)
```

#### Sample 11b

```{r}
make_correlation(data11b)
```

@@

#### Sample 10c

```{r}
uva <- EGAnet::UVA(data = data10c, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 11a

```{r}
uva <- EGAnet::UVA(data = data11a, cut.off = 0.3)
uva
uva$keep_remove
```

#### Sample 11b

```{r}
uva <- EGAnet::UVA(data = data11b, cut.off = 0.3)
uva
uva$keep_remove
```

@@

#### Sample 10c

```{r ega10c}
#| fig-height: 20
#| fig-width: 12

egas10c <- make_egas(data10c)
egas10c$p
```

#### Sample 11a

```{r ega11a}
#| fig-height: 20
#| fig-width: 12

egas11a <- make_egas(data11a)
egas11a$p
```

#### Sample 11b

```{r ega11c}
#| fig-height: 20
#| fig-width: 12

egas11b <- make_egas(data11b)
egas11b$p
```

@@

#### Sample 10c

patchwork::wrap_plots(lapply(egas10c$egas, plot), nrow = 3)
```

#### Sample 11a

patchwork::wrap_plots(lapply(egas11a$egas, plot), nrow = 3)
```

#### Sample 11b

patchwork::wrap_plots(lapply(egas11b$egas, plot), nrow = 3)
```

@@

#### Sample 10c

```{r}
n <- parameters::n_factors(data10c, n_max = 12)

#### Sample 11a

```{r}
n <- parameters::n_factors(data11a, n_max = 12)

#### Sample 11b

```{r}
n <- parameters::n_factors(data11b, n_max = 12)
